Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-04-25 WRITEUP/ms.tex
up to sec 6

Given the stochastic nature of \flower in its star formation history, we mostly focus on
two of its most extreme evolutionary stages in this work (see \Sec{singless}).
These phases correspond to (a) an intensely accreting phase and
(b) a starburst phase (\Fig{SFH}). We are interested in determining whether 
MCC properties are sensitive to these different dynamical
conditions. For completeness, we also show the scaling relations examined for the other evolutionary stages 
traced in the simulation (see \Sec{ncut}). 
In \Sec{rot}, we examine the importance of rotation support in the MCC dynamics and
discuss the implication of this finding in \Sec{rotDiss}.

@@

% This is the messy stage 
\begin{figure*}[htbp]
 \centering
  \includegraphics[scale=0.6]{\figpath/{dual_16_ncut_0.53}.pdf}
  \\ [-2.9em]
  \includegraphics[scale=0.6]{\figpath/{dual_16_ncut_6.81}.pdf}
  \\ [-2.9em]
  \includegraphics[scale=0.6]{\figpath/{dual_16_ncut_18.96}.pdf}
\caption{
Examples of MCCs (white contours) identified by the clump finder in
\flower during its accreting phase, where \flower is dispersion-dominated.
Colorbar on the right shows the mean
H$_2$ number density, weighted by gas mass. Different rows show the results obtained by applying different H$_2$ number density cuts $(n_{\rm cut})$ as shown by the label. Left and right panels show the galaxy from different viewing angles.
\label{fig:MCC}}
\end{figure*}

@@

To visually display 
the clump finding procedure, in \Fig{MCC} we overplot the molecular structures identified using a subset of the H$_2$ density cuts ($n_{\rm cut}$\eq0.53, 5.81, and 18.96\,\cc) on the H$_2$ density maps.
Since the molecular structures identified could easily appear as overlapping structures depending on the viewing angle, we also plot them in different three-dimensional projections (right panels of \Fig{MCC}) so that one can more easily see that they are collections of disjoint structures.
%
We repeat this identification process for 14 evolutionary stages between redshift \z$\in$[6.0, 7.2], spaced by $\Delta t$\eq15\,Myr.

@@

% Molecular clouds are the natal place for \SF, their structure and dynamics hold important clues to understanding
% the mechanisms and physics of formation and evolution of molecular structures and \SF.
Upon identifying the molecular structures, we extract properties such
as the gas mass $M_{\rm cl}$, effective size $R$, Mach number
$\mathcal{M}$, r.m.s. velocity dispersion $\sigma$
, and gas surface density $\Sigma_{\rm gas}$ to examine their dynamics.

The mass of an MCC is calculated from the uniformly-gridded 3D density field, integrating over the MCC volume $V$. The effective size is defined assuming spherical geometry, i.e. $R \equiv (3 V /4 \pi)^{1/3}$.
The full velocity dispersion of MCCs is calculated from 
the bulk velocity field $\sigma_{\rm bulk}$, non-thermal velocity dispersion $\sigma_{\rm NT}$, and thermal sound speed $c_s$, following
\begin{equation}
\sigma^2 = \sigma_{\rm NT}^2 + \sigma_{\rm bulk}^2 + c_s^2.
\label{eqn:veldisp}
\end{equation}
%
In \obs of MCCs, the linewidth contribution of dense gas 
exceeds that from the diffuse gas. We therefore calculate each term on
the right-hand side of Equation~\ref{eqn:veldisp} as a density-weighted quantity. 
For instance, the bulk is calculated as follows
\begin{equation}
\sigma_{\rm bulk}^2 = \frac{1}{{3}}\frac{\sum_{i} \rho_i \left|\mathbf{v}_i - \mathbf{\bar v}\right|^2}{\sum_i \rho_i}\,,
\end{equation}
where the sum is done for the cells composing each MCC.
Similarly, the non-thermal velocity dispersion is calculated as follows
\begin{equation}
\sigma_{\rm NT}^2 = \frac{\sum_{i} \rho_i \left(P_{\rm NT, i}~k_B / M_p / <\rho_i> \right)^2}{\sum_i \rho_i}\,,
\end{equation}
and the thermal sound speed is calculated through
\begin{equation}
%        x = (self.Pressure * self.k_B_erg / C.m_p.cgs.value) / self.avg_density
c_s^2 = \frac{\sum_{i} \rho_i \left(P_i~k_B / M_p / <\rho_i> \right)^2}{\sum_i \rho_i}\,,   % so that cs^2 has dimension of [erg/g]
\end{equation}
where $P_{\rm NT, i}$ and $P_i$ are the non-thermal and thermal pressures of cell $i$ in units of [K\,\cc], respectively, $k_B$ is the Boltzmann constant, and 
$M_p$ is the mass of a proton.

@@

The highest density threshold of $n_{\rm cut}$\eq31.62\,\cc corresponds to 
a minimum MCC mass of the order of 10$^{5.5}$\,\Msun for the densest structure.
However, not all evolutionary stages considered have at least one MCC at this highest density threshold, 
we therefore consider MCCs identified with the second highest density threshold ($n_{\rm cut}$\eq18.96\,\cc) in the following. 
We show in \Fig{dist} the MCC distribution in terms of their molecular gas mass, radius, and gas mass fraction, which we define as
\begin{equation}
f_{\rm gas} = \frac{M_{\rm cl}} {\left(M_{\rm cl} + M_\star\right)}.
\end{equation}
%
We note that the distributions vary for different evolutionary stages of \flower. 
%
The massive ($M_{\rm cl}>$10$^8$\,\Msun) 
clouds identified at low density cut (see top left panel of \Fig{dist})  
correspond to the molecular disk of the
galaxy, which is identified as a single component for low $n_{\rm
  cut}$. Overall, the mass of all MCCs identified ranges between $M_{\rm
  cl}\simeq$10$^{5.5-8.5}$\,\Msun, which is comparable to those observed in
\z$\sim$2 galaxies in rest-frame UV and optical light
\citep{Elmegreen07a, Elmegreen09a}. The stellar-to-gas mass ratio ranges between $M_{\star}/M_{\rm cl} \simeq$\,0.1\,--\,100 over all the
MCCs identified across all evolutionary stages of \flower (see e.g., \Fig{stellarRatio16}).

@@

\begin{figure}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/Mach_pressure-stellar-to-gas_ss21-ss27.png}
\caption{
Mach number derived from the pressure of MCCs as a function of their stellar-to-gas mass ratio in four evolutionary stages, as denoted in the panels.
% ss20,21,22,27
The Mach number of MCCs with $M_\star/M_{\rm cl} \simeq 0.1 - 1$ increases as \SF proceed in \flower. In that bottom panel, the 
light blue symbols correspond to MCCs in the satellites in the outskirt of \flower and are identified with low $n_{\rm cut}$.
\DL{replace w/ non-thermal velocity versus bulk velocity plot to investigate importance of differential rotation in the derived velocity dispersion.}
\label{fig:Mach_stellarRatio}}
\end{figure}

@@

We present results on the two most extreme evolutionary stages of \flower\ --- the accreting and starburst phases (see \Sec{sfh}), 
and identify a set of MCCs in each of them. 
Scaling relations for the MCCs are shown in \Fig{larsons_single} for the accreting (left panels) and starburst phase (right panels), respectively.

Focusing on the accreting phase, MCCs in \flower\ are characterized by large velocity dispersions ($\sigma \simeq 100 {\rm km s}^{-1}$) 
and sizes ($R\simeq 100$\,pc). These values are consistent with those found in starburst galaxies, 
such as the nearby gas-rich galaxy M64 and 
% Kennicutt, 1996IAUS..171...11K
% Spiral gal, appears to have accreted a gas-rich companion in the recent past, 
% with the inner gas disk the remnant of the
% original disk (Braun et al. 1992; Rubin 1994; Rix et al. 1995). 
the $z$\ssim2 starbursting disk galaxy SMM\,J2135-0102 % SFR: 400, fgas ~ 0.6.
\citep{Rosolowsky05a, Swinbank11a}, but are higher than those found in the Milky Way and extragalactic GMCs \citep{Heyer04a, Bolatto08a}.

% middle
While the virial parameter is typically defined as Equation~\ref{eqn:alpha} in observational studies, as they probes structures that are 
mainly composed of molecular gas only, we calculate the virial parameter including the influence from the stellar component 
for MCCs of \flower (i.e., $\alpha_{\rm vir, tot}$ via Equation~\ref{eqn:alpha_tot}) given the high stellar-to-gas mass ratios of 
some of them (see \Fig{stellarRatio16}). 
MCCs with the highest stellar-to-gas mass ratio ($\gtrsim$\,1) correspond to the central main disk of \flower (see top panels of 
\Fig{MCC} and \Sec{distribution}), which includes a large fraction of stellar mass that are already assembled in \flower. 
This explains the low total virial parameter seen in the most massive MCCs of \flower in this phase, as shown in
the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential influence the overall stability of such MCCs.

% PVE
Motivated by observational studies, we also plot the $\sigma^2/R$ ratio and gas surface density of MCCs in the bottom left panel of \Fig{larsons_single}.
In the same plot, we show those observed in the Galactic Ring Survey (GRS) of the Milky Way \citep{Heyer09a} for comparison.
Dashed lines in the figure show the loci along which the corresponding external pressures are needed for MCCs in equilibrium to have certain 
linewidths for a given set of surface densities (see \Sec{PVE}).
% (Rice+16) find variation in $V_0^2$, where they find larger linewidths for GMCCs in inner galactic disk, but they find that the clouds in the Galactic disk are still consistent with SVE (see also Solomon87a ; cf. Heyer+09).

% cloud structures at large and small scale
% Larson's: m = 460 M_sun (r_pc)^1.9 for structure w/in molecular clouds. --> $m \propto r^2$ \citep{McKee07a} (law of constant
% column density) as fundamental properties of molecular cloud structure.
Larson's third relation relates MCC structures on small and large
scales via mass and size \citep{Larson81a,
  McKee07a}. Since cloud mass in observational studies is sometimes derived by integrating over the mass surface density, 
which is related to the column density ($N_H$) that is obtainable from extinction maps ($A_V$), the mass-size relation is 
also known as the constant column density relation. 
\MM{And is thus inconsistent with the variation in $\sigma^2/R$ with
  $\Sigma$.  Effectively, Larson's mass-size relation is a single
  point on that relationship, at the constant $\Sigma$ value.  This
  suggests that the mass-size relation is just an artifact of the
  narrow range of column densities observed with $^{12}CO$, as
  suggested among others by \citet{Ballesteros11}.}
  \DL{will discuss implication in \Sec{MR}.}
By assuming dust properties from \citet[][]{weingartner:2001}, extinction for a cloud with Milky Way-like dust can be written as 
\begin{equation}
A_V = \frac{N_H}{1.8 \times 10^{21} {\rm cm}^{-2}}\,,
\end{equation}
Assuming spherical symmetry, the mass of an MCC can then be expressed as a function of $A_V$ and its size $R$
\begin{equation}\label{eqn:constantcolumndensity}
M_{\rm cl} = \frac{4\pi}{3} \mu m_p n R^3 = 154~A_v \left(\frac{R}{\rm pc}\right)^2 \Msun \,,
\end{equation}
where we adopt $\mu = 2.5$ as the mean molecular weight.

We show in \Fig{MR} the size-mass relation of the MCCs of \flower compared to observational data of molecular clouds associated with massive \SF in the 
Milky Way \citep{Beuther02a, Mueller02a, Hill05a, Motte07a} and an empirical relation obtained for massive \SF based on Milky Way clouds ($<$10\,\Msun; \citealt{Kauffmann10b, Kauffmann10c} and references therein): $M \gtrsim 870(R/{\rm pc})^{4/3} M_\odot$.
Motivated by \obs, we overplot lines of constants $A_V$ in the same plot.
MCCs of \flower spans a 
 lie along the locus of $A_V \simeq 8.9$ clouds observed by
\citet{Lombardi10a} in the MW. 
\MM{Does the variation in surface
  density seen in Figure 7 correspond to the variation in $A_V$ seen
  here?}
%
%The values of $A_V$ inferred from http://adsabs.harvard.edu/abs/2017MNRAS.471.5018Fthe $M_{\rm cl}$-size relation is consistent with the extinction inferred from gas clumps analysing the UV and IR emission of \flower~by calculating the effect of radiative transfer through dust \citep[][in particular see Fig. 5 therein]{Behrens18a}

% Starburst 
In the starburst phase, MCCs have velocity dispersion, sizes,
and virial parameter comparable to those in the accreting phase; however, the MCCs in the starburst phase span 
a wider range in $\sigma^2/R$ and gas surface density. 
Due to a time delay between cloud collapse and \SF, we also examine the virial parameter of MCCs in the pre-starburst phase. 
As shown in \Fig{alphaEvol}, the total virial parameter (blue dots in the figure) 
of a subset of MCCs in the pre-starburst phase are lower than those in the starburst phase of the same mass range, which is as expected.
%Similarly, the stellar-to-gas mass ratio of MCCs in the starburst phase is higher overall (see bottom panels of \Fig{alpha21-22}).
%These trends are as expected in the MCC properties prior to and during a starburst. 
% None of these MCCs are in the unstable regime ($alpha_{\rm vir} < 2$) because the MCCs are not directly the collapsing structures, 
% i.e., we haven’t reached those scales where true collapse is happening. 
% This implication of this is that to examine the truly star-forming structures (cores) will require resolution smaller than ~40 pc.
As shown in \Fig{Mach_stellarRatio}, the Mach number (see Equation~\ref{eqn:MPress}) 
of MCCs with a stellar-to-gas mass ratio of $M_\star/M_{\rm gas} \simeq 0.1 - 1$ 
(i.e., excluding the main component of \flower with $M_\star/M_{\rm gas} \gtrsim 1$; see e.g., \Fig{stellarRatio16})
increases from the pre-starburst phase through the post-starburst phase. 
This results as stellar feedback injects kinetic energy into the surrounding ISM in the form of turbulence as \SF proceed.
In the quiescent phase, high Mach number are seen in mostly MCCs identified with the lowest density threshold. These 
correspond to satellites MCCs in the outskirts of \flower.

@@

We investigate possible variations in the dynamics of the molecular structures of \flower to test the robustness of our results against the 
choice of density threshold by adopting different sets of $n_{\rm cut}$ in identifying the MCCs. That is, how sensitive are the structure properties, and thus, 
the results presented in \Sec{singless} dependent on the choice of density thresholds.
The sizes of MCCs are dependent on the choice of $n_{\rm cut}$, 
and thus, some of the MCCs within the main disk break into multiple sub-MCCs at higher $n_{\rm cut}$. 
For instance, the cluster of points found at the lowest density threshold, 
occupying the top right corner of the linewidth-size relation in the top left panel of \Fig{alpha16-28}, 
are broken down into sub-MCCs at the highest density threshold (see top right panel of the same figure\footnote{Note
that while the biggest MCCs are broken into sub-MCCs at higher $n_{\rm cut}$, MCCs identified at lower density in the outskirts of \flower
typically do not reach the density thresholds as $n_{\rm cut}$ increases. Hence, there are fewer MCCs at the highest density threshold.} ). 
These sub-MCCs are smaller in size, and thus, are shifted leftward in the top right panel. 
In this way, we identify a population of denser molecular structures (see \Fig{MCC}). 
On the other hand, the gas velocity dispersion $\sigma$ is rather insensitive to the actual value of $n_{\rm cut}$.
%% 
%We vary the choice of H$_2$ density for each of the evolutionary stages and find no obvious differences in our results, i.e., inferences on the dynamics of \z$\sim$\,6 MCCs in relation to those observed in nearby and \z$\sim$2 galaxies in the context of cloud scaling relations.
%%
%In addition, for the densest MCC in the main disk of \flower, we find that while its size decreases as we increase $n_{\rm cut}$ --- as one would intuitively expect, the velocity dispersion remain approximately $\sigma\simeq$\,200\,\kms (see also \Fig{larsons_single}).
%%
This lack of variation is reassuring, i.e., our inferences on the dynamics of \z$\sim$\,6 MCCs in relation to those observed in 
nearby and \z$\sim$2 galaxies in the context of linewidth-size relations are not artifacts or biased by our choice of $n_{\rm cut}$ in this work.

@@

% temporal evolution in Cloud Dynamics
We show the properties of all MCCs identified across all evolutionary stages in \Fig{alpha16-28}. 
We find no quantitative differences in the cloud properties over the 700\,Myr traced in our simulation.

% Also mentioned in \Sec{sfh}, we will frame the remainder of this work focusing on the properties of MCCs identified in the two most extreme 
% evolutionary stages of \flower.

@@

Excluding the biggest MCC identified in each evolutionary stage (i.e., the top right cluster of points in the 
linewidth-size relation of \Fig{larsons_single} and the top left panel of \Fig{alpha16-28}), which correspond to 
the main disk of \flower, the MCCs of \flower have dynamics largely similar to those observed in
$z$\ssim2 spatially resolved studies of gas-rich star-forming
galaxies, in terms of their velocity dispersions, sizes, and gas
surface densities (\Fig{larsons_single}; see e.g.,
\citealt{Swinbank11a}), with sizes of the order of $R\simeq$\,100\,pc
and velocity dispersions of $\sigma\simeq$\,20$-$80\,\kms. 
Their velocity dispersions are also comparable to those observed in the inner Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a}), which lies along the locus of $\sigma\propto R^{0.56}$. Such high velocity dispersions and surface densities are expected since they are located in the nuclear regions of the galaxy, where the potential well is also deep. The higher velocity dispersions
(see footnote~\ref{ftn:veldisp} on page \pageref{ftn:veldisp}) of
these MCCs can also be understood as they have experienced more recent
episodes of \SF as \flower is assembling its stellar mass --- these MCCs have higher stellar-to-gas mass ratios of $M_\star/M_{\rm gas}\simeq0.1 - 1$ (\Fig{stellarRatio16}) and high turbulent pressure as shown by the high $\mathcal{M}$ in \Fig{Mach_stellarRatio}.  
%
In fact, by the accreting stage (see \Fig{SFH}a) at $z\simeq$\,7.2, 
\flower has assembled a stellar mass of
$M_\star$\eq7.5\E{9}\,\Msun.

>>>>

Given the stochastic nature of \flower in its star formation history, we mostly focus on
two of its most extreme evolutionary stages in this work (see \Sec{singless}).
These phases correspond to (a) an intensely accreting phase and
(b) a starburst phase (\Fig{SFH}). We are interested in determining whether 
MCC properties are sensitive to these different dynamical
conditions. For completeness, we also show the scaling relations examined for the other evolutionary stages 
traced in the simulation (see \Sec{ncut}). 
In \Sec{rot}, we investigate the importance of rotation support from large-scale motions in the MCC dynamics by comparing their properties 
in the disturbed phase of \flower and in the disk-like ordered phase.

@@

% This is the messy stage 
\begin{figure*}[htbp]
 \centering
  \includegraphics[scale=0.6]{\figpath/{dual_16_ncut_0.53}.pdf}
  \\ [-2.9em]
  \includegraphics[scale=0.6]{\figpath/{dual_16_ncut_6.81}.pdf}
  \\ [-2.9em]
  \includegraphics[scale=0.6]{\figpath/{dual_16_ncut_18.96}.pdf}
\caption{
Examples of MCCs (white contours) identified by the clump finder in
\flower during its accreting phase (\Fig{SFH}a), where \flower is dispersion-dominated.
Colorbar on the right shows the mean
H$_2$ number density, weighted by gas mass. Different rows show the results obtained by applying different H$_2$ number density cuts $(n_{\rm cut})$ as shown by the label. Left and right panels show the galaxy from different viewing angles.
\label{fig:MCC}}
\end{figure*}

@@

To visually display 
the clump finding procedure, we overplot the molecular structures identified using a subset of the H$_2$ density cuts ($n_{\rm cut}$\eq0.53, 5.81, and 18.96\,\cc) on the H$_2$ density maps (\Fig{MCC}).
Since the molecular structures identified could easily appear as overlapping structures depending on the viewing angle, we also plot them in different three-dimensional projections (right panels of \Fig{MCC}) so that one can more easily see that they are collections of disjoint structures.
%
We repeat this identification process for 14 evolutionary stages between redshift \z$\in$[6.0, 7.2], spaced by $\Delta t$\eq15\,Myr.

@@

% Molecular clouds are the natal place for \SF, their structure and dynamics hold important clues to understanding
% the mechanisms and physics of formation and evolution of molecular structures and \SF.
Upon identifying the molecular structures, we extract properties such
as the gas mass $M_{\rm cl}$, effective size $R$, Mach number
$\mathcal{M}$, velocity dispersion $\sigma$
, and gas surface density $\Sigma_{\rm gas}$ to examine their dynamics.

The mass of an MCC is calculated from the uniformly-gridded 3D density field, integrating over the MCC volume $V$. The effective size is defined assuming spherical geometry, i.e. $R \equiv (3 V /4 \pi)^{1/3}$.
The full velocity dispersion of MCCs is calculated from 
the bulk velocity field $\sigma_{\rm bulk}$, non-thermal velocity dispersion $\sigma_{\rm NT}$, and thermal sound speed $c_s$, following
\begin{equation}
\sigma^2 = \sigma_{\rm NT}^2 + \sigma_{\rm bulk}^2 + c_s^2.
\label{eqn:veldisp}
\end{equation}
%
In \obs of MCCs, the linewidth contribution of dense gas 
exceeds that from the diffuse gas. We therefore calculate each term on
the right-hand side of Equation~\ref{eqn:veldisp} as a density-weighted quantity. 
For instance, the bulk velocity dispersion is calculated as follows
\begin{equation}
\sigma_{\rm bulk}^2 = \frac{1}{{3}}\frac{\sum_{i} \rho_i \left|\mathbf{v}_i - \mathbf{\bar v}\right|^2}{\sum_i \rho_i}\,,
\end{equation}
where the sum is done for the cells composing each MCC.
Similarly, the non-thermal velocity dispersion is calculated as follows
\begin{equation}
\sigma_{\rm NT}^2 = \frac{\sum_{i} \rho_i \left(P_{\rm NT, i}~k_B / M_p / {\bar \rho_i} \right)^2}{\sum_i \rho_i}\,,
\end{equation}
and the thermal sound speed is calculated through
\begin{equation}
%        x = (self.Pressure * self.k_B_erg / C.m_p.cgs.value) / self.avg_density
c_s^2 = \frac{\sum_{i} \rho_i \left(P_i~k_B / M_p / {\bar \rho_i} \right)^2}{\sum_i \rho_i}\,,   % so that cs^2 has dimension of [erg/g]
\end{equation}
where $P_{\rm NT, i}$ and $P_i$ are the non-thermal and thermal pressures of cell $i$ in units of [K\,\cc], respectively, $k_B$ is the Boltzmann constant, and 
$M_p$ is the mass of a proton.

@@

The highest density threshold of $n_{\rm cut}$\eq31.62\,\cc corresponds to 
a minimum MCC mass of the order of 10$^{5.5}$\,\Msun for the densest structure.
However, not all evolutionary stages considered have at least one MCC at this highest density threshold, 
we therefore consider MCCs identified with the second highest density threshold ($n_{\rm cut}$\eq18.96\,\cc) in the following. 
We show in \Fig{dist} the MCC distribution in terms of their molecular gas mass, radius, and gas mass fraction, which we define as
\begin{equation}
f_{\rm gas} = \frac{M_{\rm cl}} {\left(M_{\rm cl} + M_\star\right)}.
\end{equation}
%
We note that the distributions vary for different evolutionary stages of \flower. 
%
The most massive ($M_{\rm cl}>$10$^8$\,\Msun) 
cloud identified at each density threshold (see top right corner of \Fig{stellarRatio16} and top left panel of \Fig{dist})  
corresponds to the molecular disk of the
galaxy, which is identified as a single component for low $n_{\rm
  cut}$. Overall, the mass of all MCCs identified ranges between $M_{\rm
  cl}\simeq$10$^{5.5-8.5}$\,\Msun, which is comparable to those observed in
\z$\sim$2 galaxies in rest-frame UV and optical light
\citep{Elmegreen07a, Elmegreen09a}. The stellar-to-gas mass ratio ranges between $M_{\star}/M_{\rm cl} \simeq$\,0.1\,--\,100 over all the
MCCs identified across all evolutionary stages of \flower (see e.g., \Fig{stellarRatio16}). 
The main disk occupying the top right corner of \Fig{stellarRatio16} has a stellar-to-gas mass ratio of $\simeq$\,50--100.

@@

@@

We first present results on the two most extreme evolutionary stages of \flower\ --- the accreting and starburst phases (see \Sec{sfh}).
Scaling relations for the MCCs identified are shown in \Fig{larsons_single} for the accreting (left panels) and starburst phase (right panels), respectively.

Focusing on the accreting phase, MCCs in \flower\ are characterized by large velocity dispersions ($\sigma \simeq 100 {\rm km s}^{-1}$) 
and sizes ($R\simeq 100$\,pc). These values are comparable to those found in starburst galaxies, 
such as the nearby gas-rich galaxy M64 and 
% Kennicutt, 1996IAUS..171...11K
% Spiral gal, appears to have accreted a gas-rich companion in the recent past, 
% with the inner gas disk the remnant of the
% original disk (Braun et al. 1992; Rubin 1994; Rix et al. 1995). 
the $z$\ssim2 starbursting disk galaxy SMM\,J2135-0102 % SFR: 400, fgas ~ 0.6.
\citep{Rosolowsky05a, Swinbank11a}, but are higher than those found in the Milky Way and extragalactic GMCs by an order of magnitude \citep{Heyer04a, Bolatto08a}.

% middle
While the virial parameter defined as Equation~\ref{eqn:alpha} is typically used in observational studies, as they are designed to probe structures that are 
composed of mainly molecular gas only, we calculate the virial parameter of MCCs including the influence from the stellar component 
(i.e., $\alpha_{\rm vir, tot}$ via Equation~\ref{eqn:alpha_tot}) given the high stellar-to-gas mass ratios of 
some of them (see \Fig{stellarRatio16}). 
MCCs with the highest stellar-to-gas mass ratio ($\gtrsim$\,1) correspond to the central main disk of \flower (see top panels of 
\Fig{MCC} and \Fig{MCC28}, see also \Sec{distribution}), which includes a large fraction of stellar mass that are already assembled in \flower. 
This explains the low total virial parameter seen in the most massive MCCs of \flower in this phase, as shown in
the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential influence the overall stability of such MCCs.

% PVE
Motivated by observational studies, we also plot the $\sigma^2/R$ ratio and gas surface density of MCCs in the bottom left panels of \Fig{larsons_single}.
In the same plot, we show those observed in the Galactic Ring Survey (GRS) of the Milky Way \citep{Heyer09a} for comparison.
Dashed lines in the figure show the loci along which the annotated external pressures are needed for any molecular clouds in equilibrium 
to have certain linewidths for a given set of surface densities (see \Sec{PVE}).
% (Rice+16) find variation in $V_0^2$, where they find larger linewidths for GMCCs in inner galactic disk, but they find that the clouds in the Galactic disk are still consistent with SVE (see also Solomon87a ; cf. Heyer+09).

Larson's third relation describes the relationship between observed masses and sizes of molecular cloud structures
\citep{Larson81a, McKee07a}.
Since cloud mass in observational studies is sometimes derived by integrating over the mass surface density, 
which is related to the column density ($N_H$), % that is obtainable from extinction maps ($A_V$), 
the mass-size relation is also known as the constant column density relation and has been 
proposed as a fundamental property of molecular clouds on different physical scales.

By assuming dust properties from \citet[][]{weingartner:2001}, extinction for a cloud with Milky Way-like dust can be written as 
\begin{equation}
A_V = \frac{N_H}{1.8 \times 10^{21} {\rm cm}^{-2}}\,,
\end{equation}
Assuming spherical symmetry, the mass of an MCC can then be expressed as a function of $A_V$ and its size $R$
\begin{equation}\label{eqn:constantcolumndensity}
M_{\rm cl} = \frac{4\pi}{3} \mu m_p n R^3 = 154~A_v \left(\frac{R}{\rm pc}\right)^2 \Msun \,,
\end{equation}
where we adopt $\mu = 2.5$ as the mean molecular weight.

We show in \Fig{MR} the size-mass relation of the MCCs of \flower compared to observational data of molecular clouds associated with massive \SF in the 
Milky Way \citep{Beuther02a, Mueller02a, Hill05a, Motte07a} and an empirical relation obtained for massive \SF based on Milky Way clouds ($<$10\,\Msun; \citealt{Kauffmann10b, Kauffmann10c} and references therein): $M \gtrsim 870(R/{\rm pc})^{4/3} M_\odot$.
Motivated by \obs, we overplot lines of constants $A_V$ in the same plot.
As shown in the figure, MCCs of \flower lie along the locus of $A_V \simeq 8.9$ clouds observed by
\citet{Lombardi10a} in the MW. 
%
%The values of $A_V$ inferred from http://adsabs.harvard.edu/abs/2017MNRAS.471.5018F
%the $M_{\rm cl}$-size relation is consistent with the extinction inferred from gas clumps analysing the UV and IR emission of \flower~by calculating the effect of radiative transfer through dust \citep[][in particular see Fig. 5 therein]{Behrens18a}

% Starburst 
Focusing on MCCs in the starburst phase, they have similar velocity dispersion and sizes 
as those in the accreting phase; however, the MCCs in the starburst phase span 
a wider range in gas surface density (bottom panels of \Fig{larsons_single}) and have lower virial parameters (thus, more susceptible to collapse).
Due to a time delay between cloud collapse and \SF, we also compare the virial parameter of MCCs in the pre-starburst phase and post-starburst phase
(\Fig{alphaEvol}).
Most MCCs in the pre-starburst phase have even lower virial parameter than in the starburst phase. On the other hand, 
the virial parameter of MCCs in the post-starburst phase is higher than in both the pre-starburst and the starburst phase. 
This is consistent with our physical intuition of gas instability leading to \SF.

@@

We investigate possible variations in the dynamics of the molecular structures of \flower to test the robustness of our results against the 
choice of density threshold by adopting different sets of $n_{\rm cut}$ in identifying the MCCs. That is, how sensitive are the structure properties, and thus, 
the results presented in \Sec{singless} dependent on the choice of density thresholds.

The sizes of MCCs are dependent on the choice of $n_{\rm cut}$, 
and thus, some of the MCCs within the main disk break into multiple sub-MCCs at higher $n_{\rm cut}$. 
For instance, the cluster of points found at the lowest density threshold, 
occupying the top right corner of the linewidth-size relation in the top left panel of \Fig{alpha16-28}, 
are broken down into sub-MCCs at the highest density threshold (see top right panel of the same figure\footnote{Note
that while the biggest MCCs are broken into sub-MCCs at higher $n_{\rm cut}$, MCCs identified at lower density in the outskirts of \flower
typically do not reach the density thresholds as $n_{\rm cut}$ increases. Hence, there are fewer MCCs at the highest density threshold.}). 
These sub-MCCs are smaller in size, and thus, are shifted leftward in the top right panel. 
In this way, we identify a population of denser molecular structures (see \Fig{MCC}). 
On the other hand, the gas velocity dispersion $\sigma$ is rather insensitive to the actual value of $n_{\rm cut}$.
%% 
%We vary the choice of H$_2$ density for each of the evolutionary stages and find no obvious differences in our results, i.e., inferences on the dynamics of \z$\sim$\,6 MCCs in relation to those observed in nearby and \z$\sim$2 galaxies in the context of cloud scaling relations.
%%
%In addition, for the densest MCC in the main disk of \flower, we find that while its size decreases as we increase $n_{\rm cut}$ --- as one would intuitively expect, the velocity dispersion remain approximately $\sigma\simeq$\,200\,\kms (see also \Fig{larsons_single}).
%%
This lack of variation is reassuring, i.e., our inferences on the dynamics of \z$\sim$\,6 MCCs in relation to those observed in 
nearby and \z$\sim$2 galaxies in the context of linewidth-size relations are not artifacts or biased by our choice of $n_{\rm cut}$ in this work.

@@

% temporal evolution in Cloud Dynamics
We show the properties of all MCCs identified across all evolutionary stages in \Fig{alpha16-28}. 
We find no quantitative differences over the 700\,Myr traced in our simulation, except 
for the virial parameter, where the most relevant phases are shown in \Fig{alphaEvol} (see \Sec{singless}).

@@

Excluding the biggest MCC identified in each evolutionary stage (i.e., the top right cluster of points in the 
linewidth-size relation of \Fig{larsons_single} and the top left panel of \Fig{alpha16-28}), which correspond to 
the main disk of \flower, the MCCs of \flower have dynamics largely similar to those observed in
$z$\ssim2 spatially resolved studies of gas-rich star-forming
galaxies, in terms of their velocity dispersions, sizes, and gas
surface densities (\Fig{larsons_single}; see e.g.,
\citealt{Swinbank11a}), with sizes of the order of $R\simeq$\,100\,pc
and velocity dispersions of $\sigma\simeq$\,20$-$80\,\kms. 
Their velocity dispersions are also comparable to those observed in the inner Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a}), which lies along the locus of $\sigma\propto R^{0.56}$. Such high velocity dispersions and surface densities are expected since they are located in the nuclear regions of the galaxy, where the potential well is also the deepest, 
and also resulting from the injection of kinetic energy from recent
\SF as \flower is assembling its stellar mass (given the high Mach numbers of MCCs).
In fact, by the accreting stage (see \Fig{SFH}a) at $z\simeq$\,7.2, 
\flower has assembled a stellar mass of
$M_\star$\eq7.5\E{9}\,\Msun.

The high pressure observed in \flower (see \citealt{Pallottini17a})
is comparable to what has been observed in local ultra-luminous IR galaxies (ULIRGs); however, the molecular clouds in the latter are concentrated within their central regions and have typical sizes of $\sim$70-100\,pc and masses on the order of $\sim$10$^9$\,\Msun \citep{Downes98a, Sakamoto08a}. In our simulated galaxy, the high pressure MCCs of \flower are found throughout the disk. This difference likely stems from the different physical mechanisms giving rise to the formation (and thus the nature) of these molecular structures.
%
For instance, in local ULIRGs, 
%mm they are likely form 
  MCCs are likely formed
by shock compression and cloud-cloud collisions 
%mm after large amounts of gas from the pair of progenitor galaxies
%are funneled toward the central region 
    that funnel large amounts of gas from the progenitor galaxies
    towards the central region
\citep{Tan00a, Wu18a}.
% Tasker09a
On the other hand, the highly turbulent structures of \flower likely result from 
extra-planar flows that are due to gas accretion onto the galaxy and SN-driven outflows \citep{gallerani:2018,kohandel:2019}.
The presence of such extra-planar flows may \MM{Do we have any
  evidence for or against this speculation? Clarify citations and
  mergers vs accretion...} also be the 
dominant mode for forming the highly supersonic massive MCCs observed
in gas-rich star-forming galaxies at $z$\ssim2 (see also e.g.,
\citealt{Swinbank11a}) --- but the observed size scales could also be biased 
high due to the resolution limit.
The constant inter-cloud collisions as gas is being accreted onto the
main galaxy 
%\MM{This is a highly dissipative process.  Hennebelle \&
%  Klessen found it could only be important in rather small galaxies.
%  Does \flower qualify?} 
would also render the MCCs gravitationally unbound (see e.g., \citealt{Dobbs11a}), 
%\MM{Dobbs
%  started with a low-density disk, and got low-density clouds. I don't
%  think that's what you have here.  Do you have any evidence for
%  inter-cloud collisions being important?}
%\DL{think okay to state as speculation since we are not drawing conclusions based on this?} 
which would be consistent with the high $\alpha_{\rm vir}$ found for the MCCs in the main disk of \flower.
